Analysis for Project

### 2021-11-11 analysis/analysis.Rmd
Remove old plot function
The original plot I had is not nearly as useful so I am getting rid of the code

```{r}
plot_mr_effects <- function(model) {
  coef_table <- tidy(model) %>%
    filter(str_detect(term, "race") & str_detect(term, "/") & !str_detect(term, "Multiracial")) %>%
    mutate(term=str_remove(term, "race"))

  #add in the placements for each single race group
  single_race <- tidy(model) %>%
    filter(str_detect(term, "race") & !str_detect(term, "/") & !str_detect(term, "Multiracial")) %>%
    select(term, estimate) %>%
    mutate(term=str_remove(term, "race"))
  x <- c(0, single_race$estimate)
  names(x) <- c("White",single_race$term)
  coef_table$lower <- NA
  coef_table$higher <- NA
  for(i in 1:nrow(coef_table)) {
    groups <- str_split(coef_table$term[i], "/")[[1]]
    temp <- diff(sort(x[groups]))/2
    coef_table$lower[i] <- -temp
    coef_table$higher[i] <- temp
  }

  ggplot(coef_table, aes(x=reorder(term, higher, mean), y=estimate, 
                         ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error))+
    geom_hline(yintercept = 0, linetype=2)+
    geom_pointrange()+
    geom_point(aes(x=reorder(term, higher, mean), y=higher, color="red"))+
    geom_point(aes(x=reorder(term, higher, mean), y=lower, color="red"))+
    coord_flip()+
    theme_bw()
}
```

```{r}
plot_mr_effects(model2)
```

```{r}
plot_mr_effects(model4)
```

@@

```{r}
temp <- plot_effect_scatter(model4)
```

>>>>

@@

```{r}
plot_effect_scatter(model4)
```
